\documentclass[a4paper,10pt]{extarticle}
\usepackage[a4paper,pdftex]{geometry}	% A4paper margins
\setlength{\oddsidemargin}{5mm}			% Remove 'twosided' indentation
\setlength{\evensidemargin}{5mm}
\usepackage[english]{babel}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{makeidx}
\usepackage{helvet}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{geometry}
\usepackage[]{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{enumitem}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=cyan,
    urlcolor=magenta,
}

\newcommand{\methodSpec}[7] {
  \vbox{
    \begin{framed}
      \noindent
      \textbf{#1}: #2 $\to$ #3\\
      \textbf{Description:} #4 \ \\
      \textbf{Precondition:} #5 \ \\
      \textbf{Postcondition:} #6 \ \\
      \textbf{Classification:} #7
    \end{framed}
  }
}

\pagenumbering{arabic}




% --------------------------------------------------------------------
% Definitions (do not change this)
% --------------------------------------------------------------------
\newcommand{\HRule}[1]{\rule{\linewidth}{#1}} 	% Horizontal rule

\makeatletter							% Title
\def\printtitle{%
    {\centering \@title\par}}
\makeatother

\makeatletter							% Author
\def\printauthor{%
    {\centering \large \@author}}
\makeatother

% --------------------------------------------------------------------
% Metadata (Change this)
% --------------------------------------------------------------------

\title{	\large \textsc{Discrete Mathematics} 	% Subtitle
		 	\\[2.0cm]								% 2cm spacing
			\HRule{0.5pt} \\						% Upper rule
			\LARGE \textbf{\uppercase{Directed Graph}}	% Title
			\HRule{2pt} \\ [0.5cm]		% Lower rule + 0.5cm spacing
}



\author{
        Perez Molina, Tomás\\
}


\begin{document}


% ------------------------------------------------------------------------------
% Maketitle
% ------------------------------------------------------------------------------
\thispagestyle{empty}		% Remove page numbering on this page

\printtitle					% Print the title data as defined above
  	\vfill
\printauthor				% Print the author data as defined above
\newpage
% ------------------------------------------------------------------------------
% Begin document
% ------------------------------------------------------------------------------



\tableofcontents
\thispagestyle{empty}
\pagebreak

\setcounter{page}{1} % Set page numbering to begin on this page

\pagebreak
\section{Assignment}
  \begin{enumerate}
    \item Specify a directed non-weighted graph.
    \item Implement and test a directed non-weighted graph with an edges linked list. Calculate the order of each operation.
    \item To test the correct functionality of the previous class:
      \begin{enumerate}[label=(\roman*)]
        \item Implement a function to load data to a graph (for both vertices and edges).
        \item Implement a function to generate a random graph.
        \item Implement a function to show the graph on screen (either a list with vertices and edges or a graph drawing).
      \end{enumerate}
    \item Implement all three traversal algorithms (Plain search, BFS and DFS)
    \item Modifying previous functions, write and test algorithms that:
      \begin{enumerate}[label=(\roman*)]
        \item Calculate the amount of sources and sinks.
        \item Verify if the graph is weakly connected.
        \item Given two vertices, verify if a path of length 2 exists between them.
        \item Implement Warshall's algorithm.
      \end{enumerate}
  \end{enumerate}

  \vspace{1cm}

\section{Specification}
  \subsection{DirectedGraph}
    \textit{Description:}
      Represents a directed non-weighted graph.

  	  \methodSpec{DirectedGraph}
      {IdMaterial x Type x Title x Author x Year}
      {Material}
      {Creates a new Material with the given data.}
      {\\o Type is either 1 or 2.
      \\o IdMAterial $\ge$ 1}
      {A Material is created.}
      {Constructor}

      \methodSpec{destroyMaterial}
      {Material}
      {void}
      {Deallocates all memory assigned to the Material.}
      {Material must exist.}
      {Memory freed.}
      {Destructor}
      \vspace{1cm}

  \subsection{Graph Related Algorithms}
    \textit{Description:}
      Algorithms related to graph theory

      \methodSpec{getSources}
      {Graph}
      {Number}
      {Given a graph returns the number of source vertices.}
      {Graph must exist}
      {Return the amount of source vertices in the graph}
      {Analyzer}

      \methodSpec{getSinks}
      {Graph}
      {Number}
      {Given a graph returns the number of sink vertices.}
      {Graph must exist}
      {Return the amount of sink vertices in the graph}
      {Analyzer}

      \methodSpec{isWeaklyConnected}
      {Graph}
      {Boolean}
      {Given a graph, checks whether it is weakly connected.}
      {Graph must exist}
      {
        \begin{itemize}
          \item True if the graph is weakly connected.
          \item False if the graph is not weakly connected.
        \end{itemize}
      }
      {Analyzer}

      \methodSpec{pathOfLengthTwoExists}
      {Graph x Vertex x Vertex}
      {Boolean}
      {Given a graph and two vertices checks if a path of length 2 exists between them in the graph.}
      {Graph and both vertices must exist}
      {
        \begin{itemize}
          \item True if a path of length two between the two vertces exists.
          \item False if a path of length two between the two vertces does not exist.
        \end{itemize}
      }
      {Analyzer}

      \methodSpec{warshall}
      {Graph}
      {Transitive Closure}
      {Given a graph calculates its transitive closure using Warshall's.}
      {Graph must exist}
      {The transitive closure must have the capability of calculating whether
      there is a path between two vertices in O(1) time.}
      {Analyzer}


\end{document}
